Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs

### 2022-02-23 paper/appendix.Rmd
Fix bound of the prediction lines

st_cap <- paste0(
  "Repartion of the", length(st_mono_trends_stable_rich_bm), " stations used in
  the data analysis.")
```

```{r st, fig.cap = st_cap}
p_st_mono_trends_stable_rich_bm
```

```{r}
range_cap <- paste0(
  "Range of variation of variables in spatial (vertical line) and temporal
  dataset for the (A) minimum and maximum values and (B) the range (i.e. maximum
    - minimum)."
)
```

@@

```{r}
cor_cap <- paste0("Correlation plot among variables for spatial and temporal
  relationships. ", "Median values over temporal series in each station were
  used for spatial relationships. ", "For temporal relationships, we used the
  temporal trends in each station. Futhermore, each station was weighted by the
  average error standard on the temporal trends of the variables.",
  " Pisc: piscivorous, Nb: number, node: node of the food-web corresponding to a
  trophic species, prop: proportion."
)
```

@@

>>>>

```{r}
range_cap <- paste0(
  "Range of variation of variables in spatial (vertical lines) and temporal
  dataset for the (A) minimum and maximum values and (B) the range (i.e. maximum
    - minimum)."
)
```

@@

```{r}
cor_cap <- paste0("Correlation plot among variables.", "Median values over time were
  used for spatial relationships. ", "For temporal model, we used the
  temporal trends in each station. Futhermore, each station was weighted by the
  average error standard on the temporal trends of the variables.",
  " Pisc: piscivorous, Nb: number, node: node of the food-web corresponding to a
  trophic species, prop: proportion."
)
```

@@

## Statistical model tables

### Temporal

```{r}
loadd(
  pred_bm_rich_mono_stable_trends,
  model_bm_rich_int_mono_stable_trends,
  model_bm_rich_int_mono_stable_trends,
  rsq_table_bm_rich_mono_stable_trends
)
```

```{r}
reg_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement())
    ) %>%
kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
      label = "reg"
      ) %>%
  kable_styling(latex_options = c("scale_down", "striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
table_rsq_tps <- rsq_table_bm_rich_mono_stable_trends %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  )
table_rsq_tps %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal and conditional squared R for temporal models."),
  label = "rsq"
      ) %>% #
  kable_styling(latex_options = c("striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

### Spatial

```{r}
loadd(
  sp_anova_table_bm_rich_mono_stable_trends,
  sp_rsq_table_bm_rich_mono_stable_trends
)
```

```{r}
sp_anova_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(.,
    booktabs = TRUE,
    row.names = FALSE,
    caption =
      paste0(
      "ANOVA results for the links among the spatial variation of community
      biomass and species richness and the one of network structure."),
  label = "aov-sp"
  ) %>%
  kable_styling(latex_options = c("scale_down", "striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
sp_rsq_table_bm_rich_mono_stable_trends %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0("Marginal and conditional $R^2$ for the spatial models."),
  label = "rsq-sp"
      ) %>% #
  kable_styling(latex_options = c("striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

### 2022-02-23 paper/manuscript.Rmd
Fix bound of the prediction lines

All the statistical models displayed low multicollinearity (Variance inflation
factor < 3, Table XX).  We visually inspected the residuals of the linear models
(TODO).

@@

fig_mat_cap <- paste0( "Using  sites of stream fishes in French streams that
  have been monitored at least 10 years, 1) we infered the food-web at each site
and each sampling event based on ontogenic food diet information for each
species and predator-prey body size ratio. 2) We computed the temporal trends
and the median of community biomass, species richness, connectance, average
trophic level and evenness of biomass at each site. 3) We then assessed the
relationships among a) temporal trends of food-web structure. We also assessed
the spatial relationships among median food-web structure while controlling for
the environmental gradient with two axis of a rotated PCA. The first axis of the
PCA is related to the stream gradient from upstream to downstream while the
second is related to enrichment (BOD) and site altitude (error on the PCA,
  station is present!!!).")

@@

@@

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure, evenness of biomass  and the one of community
biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
level (Table \@ref(tab:rsq)). The models over the spatial gradient were more performant, with
$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
\@ref(tab:rsq-sp)), $R_{cond}^2$ being the $R^2$conditional to the random effect.

@@

  tmp <- "paste(
  beta, \" (s.e) \", \" = \",
  mybeta, \" (\", myse, \"), \",

  italic(R)^2, \" = \", myrsq
  )"

str_replace_all(tmp,
  c(
    "myrsq" =  as.character(rsq),
    "mybeta" = as.character(beta),
    "myse" = as.character(se)
  )
)

@@

```{r bef, fig.cap=fig_bef_cap, out.width="50%"}
p_bef <- fig1_2$rich$log_bm_std +
  annotate("text", x = -.05, y = .3, parse = T,
    label = beta_rsq(rsq = coeff_bef["rsq"],
      beta = coeff_bef["estimate"], se =
        coeff_bef["std.error"])
   ) +
  labs(
    y = "Log community biomass (g per year)",
    x = "Log species richness (per year)"
  )

@@

We found a strong positive relationship between the temporal trends of community
biomass and the ones of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
Fig. \@ref(fig:bef), Table \@ref(tab:aov)), meaning that both temporal trends
had the same direction in average. At the sites 
where species richness decreased over time, community biomass also decreased
over time. On the other hand, at the sites where species richness increased over
time, community biomass also increased over time. Along the spatial gradient, we also
found a positive relationship between median community biomass and median
species richness, but half the strength as the temporal one
($r_\delta = `r sp_b_sest["rich"]`$).

The temporal trends of connectance were positively linked with the ones of
community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), also meaning that both
temporal trends had the same direction in average. That is, the sites where
food-web connectance decreased over time also had community biomass that
decreased over time and reversely. It suggests that communities that decreased
in biomass
over time loose generalist predators over time, as connectance measures the degree of generalism and reversely that communities
gaining biomass over time also gain generalist predators. Spatially, we also found
a positive relationship between median connectance and median species
richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observe
significant relationships between the temporal trends of connectance and the
ones of species richness (Fig. \@ref(fig:bmr)D) while we found a stong
negative relationship between median connectance and median species richness
along the spatial gradient
($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).

The temporal trends of average trophic level had a strong positive
relationship with the ones of community biomass 
($r_\delta = `r tps_bm_sest["tlvl"]`$, Fig. \@ref(fig:bmr)B, Table
\@ref(tab:aov)), meaning
that sites where community biomass decreased over time, average trophic level
decreased over time and *vice versa*. It means that in communities loosing biomass
over time, the average biomass of the food-web moved down to lower trophic level
and *vice versa*. We also found a positive relationship between
median average trophic level and median community biomass in space, but half the strength 
as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std)). The temporal trends of average
trophic level was unrelated to the ones of species richness. It suggests that in
communities either loosing or gaining species richness over time, the location of
average biomass along trophic level did not significantly change according to
species richnnes.  However, we found a strong negative relationship in space 
($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std), Table
\@ref(tab:aov-sp)).

Evenness of biomass was negatively linked to community
biomass in time and in space 
($r_\delta = `r tps_bm_sest["p_bm"]`$ and $`r sp_b_sest["p_bm"]`$ resp.; Fig.
\@ref(fig:bmr)C, Fig. \@ref(fig:std)). Regarding time, it means that food-webs that
lost biomass over time also had a more even distribution of biomass across species over
time and *vice versa*. A similar reasoning applies in space. On the
other hand, we found a positive relationship between the temporal trends of
biomass evenness and the one of species richness (Fig. \@ref(fig:bmr)F, Table
\@ref(tab:aov), $r_\delta = `r tps_r_sest["p_bm"]`$). We found the same
relationship in space, twice as strong however 
($r_\delta = `r sp_r_sest["p_bm"]`$).

@@

```{r}
fig_bm_rich_cap <- paste0(
  "Relationships between the temporal trends of food-web structure
  and the ones of community biomass (left panel) species richness (right panel).
  The lines surrounding each point display the standard errors associated to
  the estimated temporal trends. Red and black lines represent respectively
  significant relationships. The histograms display the distribution of
  response and predictive variables.")
```

```{r}
fig2 <- fig1_2
fig2$rich$log_bm_std <- NULL
fig2$rich <- map(fig2$rich,
  ~.x +
    theme(
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 8)
      )
  )
fig2$bm <- map2(fig2$bm, names(fig2$rich),
  ~ .x + theme(
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    ) +
  labs(
    y = paste0(var_replacement()[.y],
      "\ntrends (per year)"),
    x = paste0("Log biomass",
      "\ntrends (per year)"),
  )
)
# Delete redondant legend
fig2$bm[1:2] <- map(fig2$bm[1:2],
  ~ .x + theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank()
  )
  )

fig2$rich <- map(fig2$rich,
  ~ .x + theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  ) +
  labs(x = paste0("Log species richness",
      "\ntrends (per year)"))
  )
fig2$rich[1:2] <- map(fig2$rich[1:2],
  ~ .x + theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank()
  )
  )

# Add histograms
fig2$bm[[1]] <- ggMarginal(fig2$bm[[1]], type = "histogram", margins = "x")
fig2$rich[[1]] <- ggMarginal(fig2$rich[[1]], type = "histogram", margins = "both")
fig2$rich[2:3] <- map(fig2$rich[2:3], ~ggMarginal(.x, type = "histogram", margins = "y"))

@@

@@

```{r}
std_cap <- paste0(
  "Assessment of the space-for-time hypothesis. Effect of community biomass (top
  panel) and species richness (bottom panel) on food-web structure for the
temporal and spatial models. Top of
  bars display the standardized coefficients from the linear models, the lines
  around display the standard errors.")
```

```{r std, fig.cap=std_cap, fig.width=6}
#loadd(fig_std_coef)
std_table_bm_rich_mono_stable_trends %>%
  filter(
    term %in% c("log_rich_std", "log_bm_std"),
    !response %in% "piel_nind") %>%
  mutate_at(vars(term, response), ~str_replace_all(., var_replacement(
        several_lines = TRUE))) %>%
  mutate(
    type = str_to_sentence(type),
    type = factor(type, levels = c("Temporal", "Spatial"))) %>%
  ggplot(aes(y = std_estimate, x = response, fill = type)) +
  viridis::scale_fill_viridis(begin = 0.5, end = 1, discrete = TRUE) +
  facet_grid(rows = vars(term)) +
  geom_col(position = position_dodge(width = .9)) +
  geom_linerange(aes(ymin = std_estimate - stdse, ymax = std_estimate + stdse),
    position = position_dodge(width = .9)) +
  labs(x = "Response variables", y = "Standardized slopes", fill = "Model") +
  theme(legend.position = c(0.7, .1),
    legend.direction = "horizontal",
    text = element_text(size = 8), axis.text = element_text(size = 8)) +
  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Predictive variable",
      breaks = NULL, labels = NULL))
```

@@

# Tables {-}

## Statistical models

### Temporal

```{r}
loadd(pred_bm_rich_mono_stable_trends,
  model_bm_rich_int_mono_stable_trends,
  model_bm_rich_int_mono_stable_trends,
  anova_table_bm_rich_mono_stable_trends)

anova_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement())
  ) %>%
  kable(.,
    booktabs = TRUE,
    row.names = FALSE,
    caption =
      paste0(
      "ANOVA results for the links between the temporal trends of
      community biomass and the temporal trends of the network structure."
    ),
  label = "aov"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
reg_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement())
    ) %>%
kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
      label = "reg"
      ) %>%
  kable_styling(latex_options = c("scale_down", "striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
table_rsq_tps <- rsq_table_bm_rich_mono_stable_trends %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  )
table_rsq_tps %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal and conditional squared R for temporal models."),
  label = "rsq"
      ) %>% #
  kable_styling(latex_options = c("striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

### Spatial

```{r}
loadd(
  sp_anova_table_bm_rich_mono_stable_trends,
  sp_rsq_table_bm_rich_mono_stable_trends
)
```

```{r}
sp_anova_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(.,
    booktabs = TRUE,
    row.names = FALSE,
    caption =
      paste0(
      "ANOVA results for the links among the spatial variation of community
      biomass and species richness and the one of network structure."),
  label = "aov-sp"
  ) %>%
  kable_styling(latex_options = c("scale_down", "striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
sp_rsq_table_bm_rich_mono_stable_trends %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "rsq-sp"
      ) %>% #
  kable_styling(latex_options = c("striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

>>>>

All the statistical models displayed low multicollinearity (Variance inflation
factor < 3, Table SXX).  We visually inspected the residuals of the linear models.

@@

fig_mat_cap <- paste0("Using  sites of stream fishes in French streams that
  have been monitored at least 10 years, 1) we infered the food-web at each site
and each sampling event based on ontogenic food diet information for each
species and predator-prey body size ratio. 2) We computed the temporal trends
and the median of community biomass, species richness, connectance, average
trophic level and evenness of biomass at each site. 3) We then assessed the
relationships among a) temporal trends of food-web structure. We also assessed
the spatial relationships among median food-web structure while controlling for
the environmental gradient with two axis of a rotated PCA. The first axis of the
PCA is related to the stream gradient from upstream to downstream while the
second is related to enrichment (BOD) and site altitude.")

@@

```{r}
log_trends_percent <- rigal_classification %>%
  unnest(classif) %>%
  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
  select(variable, station, linear_slope, linear_slope_strd_error) %>%
  mutate(
    slp_percent = round((exp(linear_slope) - 1) * 100),
    std_err_percent = round((exp(linear_slope_strd_error) - 1) * 100)
  )
resume_log_trends <- log_trends_percent %>%
  group_by(variable) %>%
  summarise(
    mean = mean(slp_percent, na.rm = TRUE),
    sd = sd(slp_percent, na.rm = TRUE))
```

@@

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure, evenness of biomass  and the one of community
biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
level (Table SXX). The models over the spatial gradient were more performant, with
$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
SXX), $R_{cond}^2$ being the $R^2$conditional to the random effect.

@@

  if (!is.null(rsq)) {

    tmp <- "paste(
    beta, \" (s.e.) \", \" = \",
    mybeta, \" (\", myse, \"), \",
    italic(R)^2, \" = \", myrsq
    )"
str_replace_all(tmp,
  c(
    "myrsq" =  as.character(rsq),
    "mybeta" = as.character(beta),
    "myse" = as.character(se)
  )
)

  } else {

    tmp <- "paste(
    beta, \" (s.e) \", \" = \",
    mybeta, \" (\", myse, \") \" )"
str_replace_all(tmp,
  c(
    "mybeta" = as.character(beta),
    "myse" = as.character(se)
  )
)

  }

}

scale_xy_log_trends <- function(breaks = NULL, axis = "y", sep ="\n") {
  log_to_percent <- round((exp(breaks) - 1) * 100)
  labels <- paste0(breaks, sep, log_to_percent, " %")

  if(axis == "y") {
    fun <- scale_y_continuous
  } else {
    fun <- scale_x_continuous
  }

  fun(breaks = breaks, labels = labels)

@@

```{r bef, fig.cap=fig_bef_cap, out.width="50%"}
lab_log_rich <- expression(atop("Log species richness ("*m^{-2}*")","trend slope (log / % per year)"))
lab_log_bm <- expression(atop("Log community biomass ("*g.m^{-2}*")", "trend slope (log / % per year)"))

p_bef <- fig1_2$rich$log_bm_std +
  annotate("text", x = .1, y = -.5, parse = T,
    label = beta_rsq(
      rsq = coeff_bef["rsq"],
      beta = coeff_bef["estimate"],
      se = coeff_bef["std.error"]
    )
   ) +
  labs(
    y = lab_log_bm,
    x = lab_log_rich
  ) +
scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x") +
scale_xy_log_trends(breaks = c(-.4, -.2, 0, .4, .2), axis = "y", sep = " / ")

@@

We found a strong positive relationship between the temporal trends of community
biomass and the ones of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
Fig. \@ref(fig:bef)), meaning that both temporal trends
had the same direction in average. At the sites 
where species richness decreased over time, community biomass also decreased
over time. On the other hand, at the sites where species richness increased over
time, community biomass also increased over time. Along the spatial gradient, we also
found a positive relationship between median community biomass and median
species richness, but half the strength as the temporal one
($r_\delta = `r sp_b_sest["rich"]`$).

The temporal trends of connectance were positively linked with the ones of
community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), also meaning that both
temporal trends had the same direction in average. That is, the sites where
food-web connectance decreased over time also had community biomass that
decreased over time and reversely. It suggests that communities that decreased
in biomass over time loose generalist predators over time, as connectance
measures the degree of generalism, and reversely that communities
gaining biomass over time also gain generalist predators. Spatially, we also found
a positive relationship between median connectance and median species
richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observe
significant relationships between the temporal trends of connectance and the
ones of species richness (Fig. \@ref(fig:bmr)D) while we found a stong
negative relationship between median connectance and median species richness
along the spatial gradient
($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).

The temporal trends of average trophic level had a strong positive
relationship with the ones of community biomass 
($r_\delta = `r tps_bm_sest["tlvl"]`$, Fig. \@ref(fig:bmr)B), meaning
that sites where community biomass decreased over time, average trophic level
decreased over time and *vice versa*. It means that in communities loosing biomass
over time, the average biomass of the food-web moved down to lower trophic level
and *vice versa*. We also found a positive relationship between
median average trophic level and median community biomass in space, but half the strength 
as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std)). The temporal trends of average
trophic level was unrelated to the ones of species richness. It suggests that in
communities either loosing or gaining species richness over time, the location of
average biomass along trophic level did not significantly change according to
species richnnes.  However, we found a strong negative relationship in space 
($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std)).

Evenness of biomass was negatively linked to community
biomass in time and in space 
($r_\delta = `r tps_bm_sest["p_bm"]`$ and $`r sp_b_sest["p_bm"]`$ resp.; Fig.
\@ref(fig:bmr)C, Fig. \@ref(fig:std)). Regarding time, it means that food-webs that
lost biomass over time also had a more even distribution of biomass across species over
time and *vice versa*. A similar reasoning applies in space. On the
other hand, we found a positive relationship between the temporal trends of
biomass evenness and the one of species richness (Fig. \@ref(fig:bmr)F,
$r_\delta = `r tps_r_sest["p_bm"]`$). We found the same relationship in space,
twice as strong however ($r_\delta = `r sp_r_sest["p_bm"]`$).

@@

```{r}
fig_bm_rich_cap <- paste0(
  "Relationships between the temporal trends of food-web structure
  and the ones of community biomass (left panel, A, C, E) species richness (right panel, B, D, F).
  The lines surrounding each point display the standard errors associated to
  the estimated temporal trends. Red and black lines represent respectively
  significant and non-significant slopes, both lines displays prediction from
  the Ordinary Least Squares model. The histograms display the distribution of response and predictive
  variables. Labels display the unstandardised slope coefficients and their
  standard errors (see Fig. \\ref{fig:std} for the standardized coefficients).
  $R^2$ are displayed only on the right panel, as it is the same model for both
  panels.")

@@

```{r}
fig2 <- fig1_2
fig2$rich$log_bm_std <- NULL
fig2$rich <- map(fig2$rich,
  ~.x +
    theme(
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 8)
      )
  )
fig2$bm <- map2(fig2$bm, names(fig2$rich),
  ~ .x + theme(
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    ) +
  labs(
    y = paste0(var_replacement()[.y],
      "\ntrends (per year)"),
    x = lab_log_bm
  ) +
  scale_xy_log_trends(breaks = c(-.40, -.20, 0, .20, .40), axis = "x")
)
# Delete redondant legend
fig2$bm[1:2] <- map(fig2$bm[1:2],
  ~ .x + theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank()
  )
  )

fig2$rich <- map(fig2$rich,
  ~ .x + theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  ) +
  labs(x = lab_log_rich) +
  scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x")
  )
fig2$rich[1:2] <- map(fig2$rich[1:2],
  ~ .x + theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank()
  )
  )

```{r}
# Add beta and Rsq
for (i in seq_along(fig2$rich)) {

  resp_var <- names(fig2$rich)[i]

  coeff_rich <- c(
    rsq = rsq_table_bm_rich_mono_stable_trends %>%
      filter(Response == resp_var) %$%
      unlist(.[, c("R.squared")]),
    reg_table_bm_rich_mono_stable_trends %>%
      filter(response == resp_var, term == "log_rich_std") %$%
      unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")])
    ) %>%
  round(., 2)

  coeff_bm <- reg_table_bm_rich_mono_stable_trends %>%
    filter(response == resp_var, term == "log_bm_std") %$%
    unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")]) %>%
    round(., 2)

  # Add coeff:
  fig2$rich[[resp_var]] <- fig2$rich[[resp_var]] +
  annotate("text", x = -.10, y = Inf, vjust = 1, hjust = 0,
    size = 2,
    parse = T,
    label = beta_rsq(
      rsq = coeff_rich["rsq"],
      beta = coeff_rich["estimate"],
      se = coeff_rich["std.error"]
    )
  )
  fig2$bm[[resp_var]] <- fig2$bm[[resp_var]] +
  annotate("text", x = -.4, y = Inf, vjust = 1, hjust = 0,
    size = 2,
    parse = T,
    label = beta_rsq(
      rsq = NULL,
      beta = coeff_bm["estimate"],
      se = coeff_bm["std.error"]
    )
  )
}
```

```{r}
# Add histograms
fig2$bm[[1]] <- ggMarginal(fig2$bm[[1]], type = "histogram", margins = "x")
fig2$rich[[1]] <- ggMarginal(fig2$rich[[1]], type = "histogram", margins = "both")
fig2$rich[2:3] <- map(fig2$rich[2:3], ~ggMarginal(.x, type = "histogram", margins = "y"))
```

@@

```{r}
std_cap <- paste0(
  "Assessment of the space-for-time hypothesis. Effect of community biomass (top
  panel) and species richness (bottom panel) on food-web structure for the
temporal and spatial models. The bar tops display the standardized slope coefficients
from the models ($r_\\delta$), the lines around bar tops display the standard errors.")
```

```{r std, fig.cap=std_cap, fig.width=6}
#loadd(fig_std_coef)
std_table_bm_rich_mono_stable_trends %>%
  filter(
    term %in% c("log_rich_std", "log_bm_std"),
    !response %in% "piel_nind") %>%
  mutate_at(vars(term, response), ~str_replace_all(., var_replacement(
        several_lines = TRUE))) %>%
  mutate(
    type = str_to_sentence(type),
    type = factor(type, levels = c("Temporal", "Spatial"))) %>%
  ggplot(aes(y = std_estimate, x = response, fill = type)) +
  viridis::scale_fill_viridis(begin = 0.5, end = 1, discrete = TRUE) +
  facet_grid(rows = vars(term)) +
  geom_col(position = position_dodge(width = .9)) +
  geom_linerange(aes(ymin = std_estimate - stdse, ymax = std_estimate + stdse),
    position = position_dodge(width = .9)) +
  labs(
    x = "Response variables",
    y = expression(paste("Standardized slope coefficients ", r[delta])),
    fill = "Model") +
  theme(legend.position = c(0.6, .05),
    legend.direction = "horizontal",
    text = element_text(size = 8), axis.text = element_text(size = 8)) +
  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Predictive variable",
      breaks = NULL, labels = NULL))
```

@@

### 2022-02-23 paper/method_figure.Rmd
Fix bound of the prediction lines

```{r}
# get a station that represents the results 
st_var_shape <- rigal_classification %>%
  unnest(classif) %>%
  filter(variable %in% c(get_com_str_var(), "log_bm_std")) %>%
  select(station, variable, direction)  %>%
  pivot_wider(names_from = variable, values_from = direction) 
dec_representative <- st_var_shape %>%
  filter(log_bm_std == "decrease", ct_ff == "decrease", w_trph_lvl_avg == "decrease") 
```

@@

save_plot(
  get_mypath("figures/decreasing_biomass_network.pdf"),
  g,
  ncol = 3, nrow = 1,
  base_width = 7, base_height = 7)

```

@@

```{r}

test_fig_mat_met <- plot_grid(
  map_st,
  plot_grid( plot_grid(tps_bm_dec, tps_bm_inc)),
  plot_grid(plotlist = tps_dec_inc),
  nrow = 3
)
save_plot(
  test_fig_mat_met,
  base_height = 12,
  base_asp = 1.618,
  file = get_mypath("figures", "matmet.png")
)
```

>>>>

```{r}
# get a station that represents the results
st_var_shape <- rigal_classification %>%
  unnest(classif) %>%
  filter(variable %in% c(get_com_str_var(), "log_bm_std")) %>%
  select(station, variable, direction)  %>%
  pivot_wider(names_from = variable, values_from = direction)
dec_representative <- st_var_shape %>%
  filter(
    log_bm_std == "decrease",
    ct_ff == "decrease",
    w_trph_lvl_avg == "decrease")
```

@@

save_plot(
  get_mypath("figures/decreasing_biomass_network.pdf"),
  g,
  ncol = 3, nrow = 1,
  base_width = 7, base_height = 7)
```

## Plot PCA

```{r}
loadd(p_pca)
save_plot(get_mypath("figures/rotated_pca.pdf"),
  p_pca,
  ncol = 1, nrow = 1,
  base_width = 4, base_height = 4
)
```

@@
